---
title       : Developing Data Products
subtitle    : Reproducible Pitch
author      : Srinivasa
job         : Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---
Overview
========================================================
This tool is developed as a part of the course reproducible research provided in Coursera's Data Science Specialization.

The tool explores the mtcars dataset. Specifically it plots out:

1. MPG vs Displacement for different number of cylinders.
2. MPG vs Displacement for different number of carburetors.

---
Summary of mtcars
========================================================
```{r}
summary(mtcars)
library(ggplot2)
```
---


---
MPG vs Displacement by different number of Cylinders
========================================================
```{r, echo=FALSE}
gg2 <- ggplot(mtcars, aes(x=mpg, y=disp))+
  geom_point(aes(color=cyl))+
  xlab("MPG")+
  ylab("Displacement")
gg2
```

---
MPG vs Displacement by different number of Carburetors
========================================================
```{r, echo=FALSE}
gg2 <- ggplot(mtcars, aes(x=mpg, y=disp))+
  geom_point(aes(color=carb))+
  xlab("MPG")+
  ylab("Displacement")
gg2
```

---
## Thank You.